---
title: "NPS project log file"
output: github_document
---
Currently running slurm-51053955.out
# TODO
post hoc analysis - remove several scales
check why "BLBW", "PIWA", "BTNW" give problems
new covariates for DOWO

# --------------------------------------------------------------------
Assumptions/decisions:

- add covariate value inputation - some site level have no forest covariates; right now im adding zero

- parks removed: acadia is too big
                 sair is too different (open areas)
                 elro only has one forest plot

- 500 m for the radius between the sites make sense for bird home range, but is that meaningful? now using 500m

- year of environmental covariates: 2022 (site,park)
county: stastr_tab(2020)
        deb_tab(2020)
        can_tab(2020)
        div_tab(2020)
        shr_tab(2010)  !!!!!!!!!!!!
        tpa_tab(2020)

- the _yr files refer to environmental covariates being extracted each year


# Analysis flow
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### What is this document?

This document is a log file with all the steps and information needed to run and understand the NPS bird scale selection analysis, to make sure that I also understand the code!

## Get and format vegetation data

```{r site, eval=FALSE}

source("format_veg_data/get_site_data_forgroups.R")

```
        in  - data/out/NETNtib.rds
        in  - data/src/key_park.rds
        in  - data/veg_kateaaron/NETN_forest_data_2006-2023.rds
        in  - data/veg_kateaaron/NETN_tree_dens_spp_2006-2023.rds
        in  - data/veg_kateaaron/for_sites.rds

        out - data/out/for_sit2.rds
        out - data/out/site_covs_[xx]m.rds
        out - data/out/park_site.rds
        out - data/out/for_sit_coord.rds
        out - data/out/bird_site_coords.rds
        out - data/out/close_points_f.rds


```{r park, eval=FALSE}

source("format_veg_data/get_park_data.R")

```
        in  - data/veg_kateaaron/NETN_forest_data_2006-2023.rds

        out - data/out/park_covs.rds

```{r diversity for site and park, eval=FALSE}

source('format_veg_data/local_diversity.R')

```
```{r county data export, eval=FALSE}

source("format_veg_data/FIA_getdata.R")

```
```{r county format data, eval=FALSE}
source("format_veg_data/get_coun_data.R")
```
        
## Get and format bird data, and merge with vegetation data



## Run models

### Step 1
run models
```{r step 1 run, eval = FALSE}


```

get model output (betas and scales selected) to run step 2
```{r step 1 output, eval = FALSE}


```

### Step 2 
```{r step 2 run, eval = FALSE}

source("code/fit_model/step2.R")

```

```{r step 2 output, eval = FALSE}


```

## Calculations

## Figures


# ---------------------- my repository log file ---------------------

DOOOOO(ing):

- saving per sps: data, z values, model, results, meta data
"data/ana_file/{date_out}_data_{sps_loop}_Z.rds
- 

# --------------------------------------------------------------------
TO DO:

- plotar vizinhos com o cover map

( ) Kate: if genus is kept in the diversity calculations for the FIA data
( ) Kate: are these the same? siteBA_large_s, parkBA_large_s, counPER_late_s




# --------------------------------------------------------------------
Workflow:

# format_veg_data/get_site_data_forgroups.R
        in  - data/out/NETNtib.rds
        in  - data/src/key_park.rds
        in  - data/veg_kateaaron/NETN_forest_data_2006-2023.rds
        in  - data/veg_kateaaron/NETN_tree_dens_spp_2006-2023.rds
        in  - data/veg_kateaaron/for_sites.rds

        out - data/out/for_sit2.rds
        out - data/out/site_covs_[xx]m.rds
        out - data/out/park_site.rds
        out - data/out/for_sit_coord.rds
        out - data/out/bird_site_coords.rds
        out - data/out/close_points_f.rds

# format_veg_data/get_park_data.R
        in  - data/veg_kateaaron/NETN_forest_data_2006-2023.rds

        out - data/out/park_covs.rds

# format_veg_data/local_diversity.R

# format_veg_data/FIA_getdata.R

# format_veg_data/get_coun_data.R
        in  - 'data/FIA/'

        out - data/out/coun_covs.rds

# format_bird_data/2_create_data_files.R
        in  - data/out/close_points_fcovs.rds
        in  - data/NETN-forest/tree_ba_tab_park.rds
        in  - data/NETN-forest/tree_den_tab_park.rds
        in  - data/NETN-forest/stand_struc_tab_park.rds
        in  - data/FIA/out/bas_area_tot_import.rds
        in  - data/FIA/out/tree_acre_tot_import.rds
        in  - data/FIA/out/stand_struc_import.rds
        in  - data/park_raster/{pk[i]}_pb.rds
        in  - y1
        in  - visits (data/out/visits.rds)
        in  - yr_pk

        out - data/src/sites_park_tib.rds
        out - data/out/site_n_key.rds
        out - data/out/y_dat3.rds
        out - data/y_dat8.rds
        out - data/X.rds 
        out - data/sps_pk_nth.rds

# format_bird_data/back2d_covs_scales_2min_spscov.R
        in  - data/y_dat8.rds
        in  - data/X.rds
        in  - data/out/nsite_pk.rds
        in  - data/src/key_park.rds

        out - data/model_res/jags_res_{sps}_{park}_run{run_number}.rds
TODO: for now, im putting zeros in the occasions that have no environmental data (mean)

# multiple_single_sps_spscovs.R

# sbatch: nps_source.sb

# plots.R

# post_hoc


# --------------------------------------------------------------------





## Obsolete/cemetary:
# veg_maps_park.R
            in  - data/veg_maps/
            in  - data/src/key_park.rds
            in  - data/out/park_site.rds
            in  - data/out/bird_site_coords.rds
            in  - data/out/for_sit_coord.rds

------------out - data/out/key_fsite.rds 
------------out - data/out/key_bsite.rds 