---
title: "NPS project log file"
output: github_document
---
Currently running slurm-50070619.out
error running SCTA
run with less covariates for sps



## Analysis flow
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### What is this document?

This document is a log file with all the steps and information needed to run and understand the NPS bird scale selection analysis, to make sure that I also understand the code!

## Get and format vegetation data
You can include R code in the document as follows:

```{r site, eval=FALSE}

source("format_veg_data/get_site_data_forgroups.R")

```
        in  - data/out/NETNtib.rds
        in  - data/src/key_park.rds
        in  - data/veg_kateaaron/NETN_forest_data_2006-2023.rds
        in  - data/veg_kateaaron/NETN_tree_dens_spp_2006-2023.rds
        in  - data/veg_kateaaron/for_sites.rds

        out - data/out/for_sit2.rds
        out - data/out/site_covs_[xx]m.rds
        out - data/out/park_site.rds
        out - data/out/for_sit_coord.rds
        out - data/out/bird_site_coords.rds
        out - data/out/close_points_f.rds


```{r park, eval=FALSE}

source("format_veg_data/get_park_data.R")

```
        in  - data/veg_kateaaron/NETN_forest_data_2006-2023.rds

        out - data/out/park_covs.rds

```{r diversity for site and park, eval=FALSE}

source('format_veg_data/local_diversity.R')

```
```{r county data export, eval=FALSE}

source("format_veg_data/FIA_getdata.R")

```
```{r county format data, eval=FALSE}
source("format_veg_data/get_coun_data.R")
```
        


